LaMachine: A meta-distribution for NLP software

### 2019-03-21 docs/clarin_reviewer_response.md

> The paper states "Support for macOS is limited because not all participating software supports it." Could it be a solution to containerize such
> software?

One of LaMachine's flavours provides a container solution (n.b: a single container for all selected software). But on
macOS containerisation often implies virtualisation, which in fact is also already provided by LaMachine as another
flavour. That indeed offers a viable way to use software in LaMachine that is not otherwise possible on macOS (or
Windows for that matter). The statement about limited support, however, applied to compiling software for macOS
natively. I added a small footnote to hopefully clarify this.

> Is LaMachine catalogued in the VLO, with a PID to the metadata?

No, nobody has ever requested this desire yet. I'll look into it. It may be a bit difficult as LaMachine is such a
meta-distribution that it is hard to pin down for any single scenario, but it would be interesting for the services
inside a LaMachine installation.  I opened issue https://github.com/proycon/LaMachine/issues/138 to this end.

### 2019-03-28 docs/lamachine_clarin2018.tex
added first comments to clarin paper

LaMachine exists since since May 2015 and has been installed extensively ever since by numerous users. In early 2018 version 2 was
released which was a significant redesign, powered by Ansible\footnote{\url{https://www.ansible.com}}. We ourselves use
LaMachine as a means by to make our full software stack available to end-users, whether those be individual researchers, research
groups, or hosting providers like CLARIN centres. LaMachine has in fact been adopted in all of those areas. Quantifying its
actual use is not trivial despite having some tracking solutions in place, but can roughly be put at around one or two
installations or upgrades \emph{every day}. We also see a regular influx of questions on our issue tracker, indicating
community interest.

@@

>>>>

LaMachine exists since May 2015 and has been installed extensively ever since by numerous users. Our statistics show that at the minimum Lamachine was downloaded over a thousand times from over 25 different countries \footnote{https://applejack.science.ru.nl/lamastats/lamachinestats.html}. In early 2018 version 2 was
released which was a significant redesign, powered by Ansible\footnote{\url{https://www.ansible.com}}. We ourselves use
LaMachine as a means by to make our full software stack available to end-users, whether those be individual researchers, research
groups, or hosting providers like CLARIN centres. LaMachine has in fact been adopted in all of those areas. Quantifying its
actual use is not trivial despite having some tracking solutions in place, but can roughly be put at around one or two
installations or upgrades \emph{every day}. We also see a regular influx of questions on our issue tracker, indicating
community interest.

@@

Lamachine is most often used by a researcher or data scientist who installs Lamachine (locally, as a Docker or VM) on his own computer. Here we discuss two case studies where Lamachine was used under circumstances that go beyond this most common usage of Lamachine: using Lamachine on a secure server without internet connection, and using Lamachine to provide a work environment for a group of researchers.
